---
title: "2-gridworld-parallel"
format:
    html:
      toc-title: Table of contents
      toc: true
      toc-depth: 2
      code-fold: true # allow code folding
      number-sections: true
      highlight-style: github
      toc-location: body
      cap-location: top
      page-layout: full
      embed-resources: true
      self-contained-math: true
      toc-expand: true
      theme: cosmo
execute:
  echo: false        # show R code
  warning: false    # hide warnings
  message: false    # hide messages
  eval: true        # run the code
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
library(tidyverse)
library(lme4)
library(table1)
library(ggeffects)
library(jtools)
library(rempsyc)
library(emmeans)
library(ggpubr)
library(effectsize)
library(brms)
library(jsonlite)
library(purrr)
library(stringr)
library(broom)
library(ggtext)
library(sjPlot)
red <- "#D52A2A" 
blue <- "#1F77B4" 

set.seed(999)
emm_options(pbkrtest.limit = 5000)
```

```{r}
path <- "data/s2"  
files <- list.files(path, pattern = "\\.csv$", full.names = TRUE)
```

```{r}
read_one_participant <- function(file) {
  file_name <- basename(file)
  raw <- readLines(file, n = 1, warn = FALSE)

  json_text <- raw %>%
    stringr::str_replace_all("\t", ",") %>%
    stringr::str_replace_all("(\\w+):", '"\\1":')

  dat <- tryCatch(
    jsonlite::fromJSON(json_text, flatten = TRUE),
    error = function(e) {
      message("FAILED: ", file_name, " | ", conditionMessage(e))
      #writeLines(raw,  paste0("bad_raw_",  file_name, ".txt"))
      #writeLines(json_text, paste0("bad_json_", file_name, ".txt"))
      return(NULL)
    }
  )
  if (is.null(dat)) return(NULL)

  meta   <- dat$sessionMeta %>% as.data.frame()
  trials <- dat$trials %>% as.data.frame()

  dv <- trials %>%
    dplyr::filter(!is.na(dv_name) & dv_name != "null") %>%
    dplyr::select(dv_name, response) %>%
    tidyr::pivot_wider(names_from = dv_name, values_from = response)

  demo <- trials %>%
    dplyr::filter(trial_type == "survey-html-form") %>%
    dplyr::pull(response) %>%
    purrr::map(~ as.list(.)) %>%
    dplyr::bind_rows()

  cbind(file_name = file_name, meta, dv, demo)
}
```


```{r}
# Read all CSVs and combine
raw <- list.files(path, pattern = "\\.csv$", full.names = TRUE) %>%
  map_dfr(read_one_participant) %>% 
  mutate(Age=as.numeric(participantYears),
         Gender=participantGender,
         Race=participantRace,
         Ethnicity=participantEthnicity,
         agreement=as.numeric(agreement),
         commitment =as.numeric(commitment),
         anger=as.numeric(anger),
         guilt=as.numeric(guilt),
         attention =as.numeric(attention)) %>% 
  filter(Age<100) 

# one person is missing from osf 
ids <-raw$prolificID
all<-read.csv("data/s2-prolific-id.csv") %>% filter(Status == "APPROVED")
all_ids<-all$Participant.id
setdiff(all_ids, ids)

df<-raw %>% 
  filter(attention==100) #398=386=12
```

## demographics 

```{r}
table1(~ Gender + Age+  Race + Ethnicity,data=df)
```

## Descriptive stat

```{r}
table1(~ agreement + commitment + anger + guilt | repetition_condition,data=df)
table1(~ agreement + commitment + anger + guilt | payoff_condition,data=df)
table1(~ agreement + commitment + anger + guilt | payoff_condition+repetition_condition,data=df)
```

## Plot

```{r}
df_long <- df %>%
  pivot_longer(cols = c(agreement, commitment, anger, guilt),
               names_to = "DV",
               values_to = "value") %>%
  mutate(
    repetition_condition = recode(repetition_condition, "low" = "T=2", "high" = "T=6"),
    payoff_condition = recode(payoff_condition, "independent" = "Independent", "interdependent" = "Interdependent")
  ) 

# 2. Prepare Data
df_plot <- df_long %>%
  mutate(
    x_group = paste(payoff_condition, repetition_condition, sep = "_"),
    x_group = factor(x_group, levels = c("Independent_T=2", "Independent_T=6", 
                                          "Interdependent_T=2", "Interdependent_T=6"))
  )

# 3. Custom Star Function
get_stars <- function(p) {
  case_when(
    p < 0.001 ~ "***",
    p < 0.01  ~ "**",
    p < 0.05  ~ "*",
    TRUE      ~ "ns"
  )
}

# 4. Calculate Manual Stats
# A. Simple Effects
stats_simple <- compare_means(value ~ repetition_condition, data = df_plot, group.by = c("DV", "payoff_condition"), method = "t.test") %>%
  ungroup() %>%
  mutate(
    y.position = 85,
    xmin = ifelse(payoff_condition == "Independent", 1, 3),
    xmax = ifelse(payoff_condition == "Independent", 2, 4),
    p.signif = get_stars(p)
  )

# B. Main Effect
stats_main <- compare_means(value ~ payoff_condition, data = df_plot, group.by = "DV", method = "t.test") %>%
  ungroup() %>%
  mutate(
    y.position = 105, 
    xmin = 1.5, 
    xmax = 3.5,
    p.signif = get_stars(p)
  )

# 5. Define Labels (Bottom Row Only)
bottom_vars <- c("commitment", "guilt") 
label_data <- tibble(
  x = rep(c(1.5, 3.5), length(bottom_vars)), 
  y = rep(-30, 2 * length(bottom_vars)), 
  label = rep(c(paste0("<span style='color:", red, "'>Independent</span>"),
                paste0("<span style='color:", blue, "'>Interdependent</span>")), length(bottom_vars)),
  DV = rep(bottom_vars, each = 2) 
)

# 6. Plot
p <- ggplot(df_plot, aes(x = x_group, y = value, fill = payoff_condition, alpha = repetition_condition)) +
  
  # Bars (will inherit alpha)
  stat_summary(fun = mean, geom = "bar", color = "black", width = 0.7) +
  
  # Error Bars (override alpha to 1 so they are always solid black)
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.1, alpha = 1) +
  
  #geom_violin(alpha=0.4)+
  
  #stat_summary(
  #  fun = mean,
  #  fun.min = function(x) mean(x) - sd(x)/sqrt(length(x)),
  #  fun.max = function(x) mean(x) + sd(x)/sqrt(length(x)),
  #  geom = "crossbar",
  #  width = 0.3,
  #  color = "black",
  #  size = 0.7
  #) +
  
  # Stats
  stat_pvalue_manual(stats_simple, label = "p.signif", xmin = "xmin", xmax = "xmax", tip.length = 0.02) +
  stat_pvalue_manual(stats_main, label = "p.signif", xmin = "xmin", xmax = "xmax", tip.length = 0.02, bracket.size = 0.5) +
  
  facet_wrap(~ DV) +
  
  # Scales
  scale_fill_manual(values = c("Independent" = red, "Interdependent" = blue)) +
  
  # --- ALPHA SCALE NOW WORKS ---
  scale_alpha_manual(values = c("T=2" = 0.5, "T=6" = 1.0)) +
  
  scale_x_discrete(labels = c("T=2", "T=6", "T=2", "T=6")) +
  coord_cartesian(ylim = c(0, 110), clip = "off") + 
  
  # Custom Labels
  ggtext::geom_richtext(
    data = label_data, 
    aes(x = x, y = y, label = label),
    inherit.aes = FALSE,
    fill = NA, label.color = NA, size = 4.5, fontface = "bold"
  ) +
  
  theme_bw(base_size = 14) +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    panel.grid.major.x = element_blank(),
    plot.margin = margin(b = 40, t = 10, l = 10, r = 10) 
  )

print(p)

```

## analysis 

For each dependent variable, we will conduct a two-way analysis of variance (ANOVA) for each dependent variable:
- agreement ~ repetition_condition * interdependency
- commitment ~ repetition_condition * interdependency
- anger ~ repetition_condition * interdependency
- guilt ~ repetition_condition * interdependency

If the interaction is significant, simple effects will be tested using planned contrasts. If the interaction is not significant, main effects will be reported.

We will report means, standard deviations, F-statistics, p-values, partial eta squared, and 95% confidence intervals for main effects and the interaction.

```{r}
df <- df %>%
  mutate(
    repetition_condition = factor(repetition_condition,
                                  levels = c("low", "high")),
    interdependency = factor(payoff_condition,
                             levels = c("independent", "interdependent"))
  ) %>% 
  mutate(Experiment = "Experiment 2")

# pre-registeretd interaction
a_agreement <- aov(agreement ~ repetition_condition * interdependency, data = df)
a_commitment <- aov(commitment ~ repetition_condition * interdependency, data = df)
a_anger <- aov(anger ~ repetition_condition * interdependency, data = df)
a_guilt <- aov(guilt ~ repetition_condition * interdependency, data = df)


# interaction not significant 
a_agreement <- aov(agreement ~ repetition_condition + interdependency, data = df)
a_commitment <- aov(commitment ~ repetition_condition + interdependency, data = df)
a_anger <- aov(anger ~ repetition_condition + interdependency, data = df)
a_guilt <- aov(guilt ~ repetition_condition + interdependency, data = df)



# Tidy ANOVAs and add DV labels
tb <- bind_rows(
  tidy(a_agreement) %>% filter(term != "Residuals") %>% mutate(DV = "Agreement"),
  tidy(a_commitment) %>% filter(term != "Residuals") %>% mutate(DV = "Commitment"),
  tidy(a_anger) %>% filter(term != "Residuals") %>% mutate(DV = "Anger"),
  tidy(a_guilt) %>% filter(term != "Residuals") %>% mutate(DV = "Guilt")
)

# Add partial eta squared
es <- bind_rows(
  eta_squared(a_agreement, partial = TRUE,alternative = "greater"),
  eta_squared(a_commitment, partial = TRUE,alternative = "greater"),
  eta_squared(a_anger, partial = TRUE,alternative = "greater"),
  eta_squared(a_guilt, partial = TRUE,alternative = "greater")
)

# Combine effects into one data frame
tb %>%
  rename(
    Effect = term,
    F = statistic,
    p = p.value
  ) %>%
  mutate(eta2_partial = es$Eta2_partial) %>%
  select(DV, Effect, df, F, p, eta2_partial) %>% 
  nice_table(.,
             stars = TRUE,      
             #title = "ANOVA Results with Partial Eta Squared",
             #highlight = TRUE    # highlight significant rows
             )


# # Get marginal means
# library(emmeans)
# emmeans(a_agreement, ~ repetition_condition * interdependency)
# emmeans(a_commitment, ~ repetition_condition * interdependency)
# emmeans(a_anger, ~ repetition_condition * interdependency)
# emmeans(a_guilt, ~ repetition_condition * interdependency)


# # For contrasts:
# contrast(
#   emmeans(a_agreement, ~ repetition_condition * interdependency),
#   interaction = "pairwise"
# )
# 
# emmeans(a_anger, pairwise ~ repetition_condition | interdependency)
# emmeans(a_anger, pairwise ~ interdependency | repetition_condition)

```
## save data

```{r}
df %>% rename(id=file_name) %>% 
  select(-attention,-condition,-prolificID) %>% 
  write.csv(.,"data/exp2.csv")
```

## compare across studies - visal co-location effect 

```{r}
exp1<-read.csv("data/exp1.csv") %>% select(-X)
exp2<-read.csv("data/exp2.csv") %>% select(-X)
df1<- rbind(exp1,exp2)
```

```{r}
a_agreement <- aov(agreement ~ repetition_condition + Experiment + interdependency, data = df1)
a_commitment <- aov(commitment ~ repetition_condition + Experiment + interdependency, data = df1)
a_anger <- aov(anger ~ repetition_condition + Experiment+ interdependency, data = df1)
a_guilt <- aov(guilt ~ repetition_condition + Experiment+ interdependency, data = df1)

# Tidy ANOVAs and add DV labels
tb <- bind_rows(
  tidy(a_agreement)  %>% filter(term != "Residuals") %>% mutate(DV = "Agreement"),
  tidy(a_commitment) %>% filter(term != "Residuals") %>% mutate(DV = "Commitment"),
  tidy(a_anger) %>% filter(term != "Residuals") %>% mutate(DV = "Anger"),
  tidy(a_guilt) %>% filter(term != "Residuals") %>% mutate(DV = "Guilt")
)

# Add partial eta squared
es <- bind_rows(
  eta_squared(a_agreement, partial = TRUE,alternative = "greater"),
  eta_squared(a_commitment, partial = TRUE,alternative = "greater"),
  eta_squared(a_anger, partial = TRUE,alternative = "greater"),
  eta_squared(a_guilt, partial = TRUE,alternative = "greater")
)

# Combine effects into one data frame
tb %>%
  rename(
    Effect = term,
    F = statistic,
    p = p.value
  ) %>%
  mutate(eta2_partial = es$Eta2_partial) %>%
  select(DV, Effect, df, F, p, eta2_partial) %>% 
  nice_table(.,
             stars = TRUE,      
             #title = "ANOVA Results with Partial Eta Squared",
             #highlight = TRUE    # highlight significant rows
             )
```


```{r,fig.height=6.5,fig.width=6.5}
# 1. CLEAN & ORDER DATA
df_long <- df1 %>%
  pivot_longer(cols = c(agreement, commitment, anger, guilt),
               names_to = "DV_raw",
               values_to = "value") %>%
  mutate(
    # Clean up conditions
    repetition_condition = recode(repetition_condition, "low" = "T=2", "high" = "T=6"),
    payoff_condition = recode(payoff_condition, "independent" = "Independent", "interdependent" = "Interdependent"),
    
    # --- CRITICAL FIX: FORCE THE ORDER HERE ---
    # We turn the raw column (e.g., "anger") into a Factor with specific levels.
    DV = factor(DV_raw, 
                levels = c("agreement", "commitment", "anger", "guilt"), 
                labels = c("Agreement", "Commitment", "Anger", "Guilt"))
  )

# 2. Prepare Plot Data
df_plot <- df_long %>%
  mutate(
    x_group = paste(payoff_condition, repetition_condition, sep = "_"),
    x_group = factor(x_group, levels = c("Independent_T=2", "Independent_T=6", 
                                          "Interdependent_T=2", "Interdependent_T=6"))
  )

# 3. Calculate Means (Inside Bar Labels)
df_means <- df_plot %>%
  group_by(x_group, DV, Experiment) %>%
  summarise(mean_val = mean(value, na.rm = TRUE), .groups = "drop") %>%
  mutate(label = sprintf("%.1f", mean_val))

# 4. Define Stats
get_stars <- function(p) {
  case_when(p < 0.001 ~ "***", p < 0.01 ~ "**", p < 0.05 ~ "*", TRUE ~ "ns")
}

stats_simple <- compare_means(value ~ repetition_condition, data = df_plot, group.by = c("DV", "payoff_condition","Experiment"), method = "t.test") %>%
  ungroup() %>%
  mutate(y.position = 85, xmin = ifelse(payoff_condition == "Independent", 1, 3), xmax = ifelse(payoff_condition == "Independent", 2, 4), p.signif = get_stars(p))

stats_main <- compare_means(value ~ payoff_condition, data = df_plot, group.by = c("DV","Experiment"), method = "t.test") %>%
  ungroup() %>%
  mutate(y.position = 105, xmin = 1.5, xmax = 3.5, p.signif = get_stars(p))

# 5. Define Bottom Labels (Attached ONLY to "Guilt")
# We explicitly set the DV factor level to "Guilt" so it matches the data structure
label_data <- tibble(
  x = c(1.5, 3.5), 
  y = c(-40, -40), 
  label = rep(c(paste0("<span style='color:", red, "'>Independent</span>"),
                paste0("<span style='color:", blue, "'>Interdependent</span>"))),
  DV = factor("Guilt", levels = levels(df_plot$DV)) 
)

# 6. Plot
p <- ggplot(df_plot, aes(x = x_group, y = value, fill = payoff_condition, alpha = repetition_condition)) +
  
  # Bars
  stat_summary(fun = mean, geom = "bar", color = "black", width = 0.9) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.1, alpha = 1) +
  
  #The Jittered Points ---
  geom_jitter(
    width = 0.2,        
    height = 0,        
    alpha = 0.15,       
    size = 1,          
    color = "gray40"     
  ) +
  
  # Mean Labels
  geom_text(data = df_means, aes(x = x_group, y = mean_val, label = label), 
            inherit.aes = FALSE, vjust = 2, size = 3.5, fontface = "bold", color = "black") +

  # Stats
  stat_pvalue_manual(stats_simple, label = "p.signif", xmin = "xmin", xmax = "xmax", tip.length = 0.02) +
  stat_pvalue_manual(stats_main, label = "p.signif", xmin = "xmin", xmax = "xmax", tip.length = 0.02, bracket.size = 0.5) +
  
  # Faceting
  facet_grid(DV ~ Experiment, scales = "fixed", drop = FALSE) +
  
  # Scales
  scale_fill_manual(values = c("Independent" = red, "Interdependent" = blue)) +
  scale_alpha_manual(values = c("T=2" = 0.5, "T=6" = 1.0)) +
  scale_x_discrete(labels = c("T=2", "T=6", "T=2", "T=6")) +
  coord_cartesian(ylim = c(0, 110), clip = "off") + 
  
  # Bottom Labels
  geom_richtext(data = label_data, aes(x = x, y = y, label = label),
                inherit.aes = FALSE, fill = NA, label.color = NA, size = 4.5, fontface = "bold") +
  
  theme_bw(base_size = 14) +
  theme(legend.position = "none", axis.title.x = element_blank(), panel.grid.major.x = element_blank(),
        plot.margin = margin(b = 40, t = 10, l = 10, r = 10)) +
  ylab("Mean rating (0–100)")

print(p)
ggsave(
  filename = "results.png", 
  plot = p, 
  width = 6.5,       # Fits nicely on a standard page width
  height = 6.5,       # Tall enough for 4 rows of panels
  dpi = 300,         # 300 is standard print quality (use 600 for even higher)
  units = "in",
  bg = "white"       # Ensures the background isn't transparent
)
```

## agreement predict normative reactions

```{r}
a_anger <- lm(anger ~ agreement+interdependency + repetition_condition + Experiment, data = df1)
a_guilt <- lm(guilt ~ agreement+interdependency+repetition_condition + Experiment, data = df1)
tab_model(a_anger,a_guilt)

a_anger <- lm(anger ~ commitment+interdependency + repetition_condition + Experiment+ interdependency, data = df1)
a_guilt <- lm(guilt ~ commitment+interdependency+repetition_condition + Experiment+ interdependency, data = df1)
tab_model(a_anger,a_guilt)

```





